### 2022-05-18 main/chapter_2ljets.tex
expand rjr references

\subsection{RJR}
Recursive Jigsaw Reconstruction (RJR), is a method for
interpreting particle data as arising from user-specified decay trees.
The $\twoljets$ RJR analysis uses two C1N2 decay trees which are displayed in
Figure~\ref{fig:2ljets_rjr_decay_trees}.

\begin{figure}[tp]
\centering
\includegraphics[width=0.99\textwidth]{figures/2ljets_rjr_trees.pdf}
\caption{%
Decay trees for the $\twoljets$ RJR analysis.
Both diagrams represent processes also targetted in the electroweak analysis.
(left) A fully-resolved decay tree with its particles labelled.
(right) Only the $Z\rightarrow\ell\ell$ (\underline{v}ector boson)
is resolved, but the supersymmetric system recoils off
hard QCD jets labelled ``ISR'', boosting the \underline{i}nvisible particles,
to generate visibly large $\met$ in models with small mass-splittings.
The same approach is used for SR-OffShell selections in the electroweak
analysis.
}
\label{fig:2ljets_contours_gmsb}
\end{figure}

>>>>

\subsection{RJR}
The Recursive Jigsaw Reconstruction (RJR) method interprets reconstructed
particle data by reconciling them with user-specified decay trees.
Decay trees used in the $\twoljets$ RJR analysis,
displayed in Figure~\ref{fig:2ljets_rjr_decay_trees},
target C1N2-like scenarios similar to those also considered in the $\twoljets$
electroweak search.
The RJR algorithm works by making decisions of how to assign four-momenta
to different `systems' --- nodes in the decay graphs -- and evaluates event
variables in their respective rest
frames~\cite{jackson2017sparticles, jackson2017rjr}.

Since the year 2017, RJR event variables have been demonstrated as effective
for interpreting Supersymmetric particle
physics~\cite{santoni2018probing}
and used in numerous \atlas\
searches~\cite{SUSY-2016-07, SUSY-2016-15, SUSY-2016-16} \TODO{more}.

\begin{figure}[tp]
\centering
\includegraphics[width=0.9\textwidth]{figures/2ljets_rjr_trees.pdf}
\caption{%
Decay trees for the $\twoljets$ RJR analysis.
Both diagrams represent processes also targetted in the electroweak analysis.
(left) A fully-resolved decay tree with its particles labelled.
(right) Only the $Z\rightarrow\ell\ell$ (\underline{v}ector boson)
is resolved, but the supersymmetric system recoils off
hard QCD jets labelled ``ISR'', boosting the \underline{i}nvisible particles,
to generate visibly large $\met$ in models with small mass-splittings.
The same approach is used for SR-OffShell selections in the electroweak
analysis.
}
\label{fig:2ljets_rjr_decay_trees}
\end{figure}
